---
title: "R Notebook"
output:
  pdf_document: default
  html_document:
    df_print: paged
  html_notebook: default
---

Part (a)

```{r}
jobs <- c("UI", "Backend", "management", "HR", "HSE");
employ_num <- c(8,12,4,3,3);
```

Part (b)

```{r}
barplot(employ_num,xlab="employee number",ylab="jobs",main="employee distribution",names.arg = jobs,horiz = TRUE, col.main = "green", col.lab = "blue")
```

Part (c)

```{r}
UI<-c(75000,25000,48000,42000,35200,45000,23000,45500)
backend=c(20000, 80000, 36000, 46300, 41000, 43000, 22000,37000, 39000, 43500, 69000, 5000)
management=c(80000, 67000, 56000, 82000)
HR=c(45000, 39000, 30000)
HSE=c(12000, 25000, 31500)

boxplot(UI,backend,management,HR,HSE)
```

Part (d)

```{r}
quantile(UI)
quantile(backend)
quantile(management)
quantile(HR)
quantile(HSE)
```

```{r}

```

```{r}
iqr=IQR(UI,0.25)
iqr
```

```{r}
print("UI")
iqr = IQR(UI)
q2 = quantile(UI,0.5)
q3 = quantile(UI,0.75)
Tmin = q2-(1.5*iqr) 
Tmax = q3+(1.5*iqr) 
# find outlier
UI[which(UI < Tmin | UI > Tmax)]

print("backend")
iqr = IQR(backend)
q2 = quantile(backend,0.5)
q3 = quantile(backend,0.75)
Tmin = q2-(1.5*iqr)
Tmax = q3+(1.5*iqr)
# find outlier
backend[which(backend < Tmin | backend > Tmax)]

print("management")
iqr = IQR(management)
q3 = quantile(management,0.75)
Tmin = q2-(1.5*iqr)
Tmax = q3+(1.5*iqr)
# find outlier
management[which(management < Tmin | management > Tmax)]

print("HR")
iqr = IQR(HR)
q2 = quantile(HR,0.5)
q3 = quantile(HR,0.75)
Tmin = q2-(1.5*iqr)
Tmax = q3+(1.5*iqr)
# find outlier
HR[which(HR < Tmin | HR > Tmax)]

print("HSE")
iqr = IQR(HSE)
q2 = quantile(HSE,0.5)
q3 = quantile(HSE,0.75)
Tmin = q2-(1.5*iqr)
Tmax = q3+(1.5*iqr)
# find outlier
HSE[which(HSE < Tmin | HSE > Tmax)]

```

Part (e)

It seems that employees in UI group have mostly low but similar salaries and only one person has high salary.

employess in backend group have symmetric salaries, mostly like together with no one with too high or too low salary. but some people have lower or higher salaries.

All people in management and HR groups' salaries are different but have close values.

HSE employees' salaries are very different.

```{r}
library("ggplot2")


ggplot() + 
 aes(x=UI)+
 geom_histogram(aes(y=..density..), colour="black", fill="white", bins=5)+
 geom_density(alpha=.2, fill="blue") 


ggplot() + 
 aes(x=backend)+
 geom_histogram(aes(y=..density..), colour="black", fill="white", bins=5)+
 geom_density(alpha=.2, fill="blue")



ggplot() + 
 aes(x=management)+
 geom_histogram(aes(y=..density..), colour="black", fill="white", bins=4)+
 geom_density(alpha=.2, fill="blue")


ggplot() + 
 aes(x=HR)+
 geom_histogram(aes(y=..density..), colour="black", fill="white", bins=3)+
 geom_density(alpha=.2, fill="blue")


ggplot() + 
 aes(x=HSE)+
 geom_histogram(aes(y=..density..), colour="black", fill="white", bins=3)+
 geom_density(alpha=.2, fill="blue")

```

Part (f)

```{r}
# install.packages("lessR")
library(lessR)

cat_var <- cut(c(UI,backend,management,HR,HSE), breaks = c(-Inf,20000,30000,40000,50000,Inf), labels = c("very low", "low","middle","high","very high"), format_fun = scales::percent)

# Store the variable as data frame
cat <- data.frame(cat_var)

# Pie
cols <-  hcl.colors(length(levels(cat_var)), "Fall")
PieChart(cat_var, data = cat, hole = 0,
         fill = cols,
         labels_cex = 0.6) 
 
```

Part (g)

```{r}
# Create the function.
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}

mean(backend)
median(backend)
getmode(backend)
var(backend)
sd(backend)
```
