---
title: "Question 8"
output:
  html_document:
    df_print: paged
---

Part (a)

```{r}
scores <- c(57, 66, 72, 78, 79, 79, 81, 81, 82, 83, 84, 87, 88, 88, 89, 90, 91, 92, 94, 95)
scores
```

Part (b)

```{r}
# Create the function.
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}

mean(scores)
median(scores)
getmode(scores)
var(scores)
sd(scores)
```

Part (c)

First, we should calculate the IQR range and multiply it by 1.5.

```{r}
quantile(scores)
```

IQR = quantile3 - quantile2 = 10.25

IQR \* 1.5 = 15.3

now we calculate the range [quantile2-15.3,quantile3+15.3) which will be

[79-15.3,89.25+15.3] = [63.7,104.55]

so by checking the scores vector, 57 is the only number that is not in this range, so it's the only outlier.

Part (d)

```{r}
boxplot(scores)
```

Part (e)

```{r}
k <- ceiling(1 + 3.322*log10(length(scores)))
ggplot() + 
 aes(x=scores)+
 geom_histogram(aes(y=..density..), colour="black", fill="white", bins=5)+
 geom_density(alpha=.2, fill="blue") 
```

scores seem to be right skewed and mostly have high values

mean is more than median

because the lower numbers aren't so low to reduce the mean.

median is better center value when the data is righ or left skewed and have outliers.

when using median, it's best to choose IQR for finding data spread.
